SBML L3 paper response to reviewers

### 2020-01-01 main.tex
More text

@@

@@

@@

To help connect the sections better, we have expanded the final paragraph in the introduction to provide a preview of the remaining sections, and then in other places, we added phrases referencing different sections in order to try to connect the sections better.

>>>>

Thank you for pointing out the potential for misunderstanding.  In the revised version of the manuscript, we have edited the abstract to clarify that SBML Level~3 has already been in some use, and that this is not an entirely new development.  With respect to the title, we have tried to find an alternative, but could not find one that did not leave open the possibility of \emph{other} misinterpretations or misunderstandings.  We feel the title, while imperfect, is still the best we can do for a review article like this, and we hope the changes to the abstract are enough to avoid potential misunderstanding.

@@

We have updated the manuscript to emphasize that some other smaller changes have been made, though the modularity is the main change.  These points are made in a new paragraph at the end of the section titled ``The structure of SBML''.

@@

The goal of the manuscript is to describe the possibilities that SBML offers, but we did not intend to gloss over difficulties or problems.  The manuscript already mentioned some related standards, and we have now tried to clarify the relationships better in the edited second paragraph of the section titled ``Impact of SBML''.  Since a comparison to other formats is not the focus of the paper, and the journal's paper guidelines have length limitations, we hope this compromise is good enough.  With respect to journals, we have added text to the manuscript mentioning journal and funding agency guidelines.  We have also added more discussions of difficulties involving SBML.  These changes are in the second-to-last paragraph of the section titled ``Impact of SBML'' and the last three paragraphs of the section titled ``Forthcoming challenges''.

@@

To help connect the sections better, we have expanded the final paragraph in the introduction to provide a preview of the remaining sections, and in other parts of the text, we have added phrases referencing different sections in order to try to connect the sections better.
